---
title: "Google Play Store"
# author: "Vinoth Shankar"
# Student ID: "C00246396"
# date: "April 29, 2020"
output: 
  flexdashboard::flex_dashboard:
    source_code: "https://github.com/vinothshankar/PlayStore_InteractiveDashboard"
    vertical_layout: scroll
    theme: yeti
---

```{r setup, include=FALSE}
#Loads necessary packages to run Dashboard
library(flexdashboard)
library(tidyverse)
library(highcharter) 
library(lubridate)
library(stringr)
library(xts)
library(plotly)
library(viridis)
library(rjson)
library(crosstalk)
library(DT)

```

```{r include=FALSE}

#Loading and Cleaning the data
data<-read.csv("./googleplaystore.csv")
df1<-data

#Cleaning the data and converting the columns to required format
data.clean <- data %>%
  mutate(
    # Eliminate some characters to transform Installs to numeric
    Installs = gsub("\\+", "", as.character(Installs)),
    Installs = as.numeric(gsub(",", "", Installs)),
    # Eliminate M to transform Size to numeric
    Size = gsub("M", "", Size),
    # Replace cells with k to 0 since it is < 1MB
    Size = ifelse(grepl("k", Size), 0, as.numeric(Size)),
    # Transform reviews to numeric
    Reviews = as.numeric(Reviews),
    # Remove currency symbol from Price, change it to numeric
    Price = as.numeric(gsub("\\$", "", as.character(Price))),
    # Last Updated to date format
    Last.Updated = mdy(Last.Updated),
    # Replace "Varies with device" to NA since it is unknown
    Min.Android.Ver = gsub("Varies with device", NA, Android.Ver),
    # Keep only version number to 1 decimal
    Min.Android.Ver = as.numeric(substr(Min.Android.Ver, start = 1, stop = 3)),
    # Drop old Android version column
    Android.Ver = NULL
  ) %>%
  filter(
    # Two apps had type as 0 or NA, they will be removed 
    Type %in% c("Free", "Paid")
  )
#Removing duplicate rows
data<-data.clean %>%
  distinct()
```

``` {js}
// Inverse color of navigation bar.
$('.navbar-inverse').removeClass('navbar-inverse').addClass('navbar-default');
```

```{r include=FALSE}
# Create a custom theme for the plots. 
thm <- hc_theme_merge(
  hc_theme_darkunica(),
  hc_theme(
    chart = list(
      backgroundColor = "transparent",
      divBackgroundImage = "https://wallpaperaccess.com/full/1650624.jpg"
    ),
    title = list(
      style = list(
        color = 'white',
        fontFamily = "Open Sans"
      )
    )
  )
)

thm_dark <- hc_theme_merge(
  hc_theme_darkunica(),
  hc_theme(
    chart = list(
      backgroundColor = "transparent",
      divBackgroundImage = "https://www.hdwallpapers.net/previews/android-logo-786.jpg"
    ),
    title = list(
      style = list(
        color = '#2B908F',
        fontFamily = "Open Sans"
      )
    )
  )
)
dark <- hc_theme_merge(
  hc_theme_darkunica(),
  hc_theme(
    chart = list(
      backgroundColor = "transparent",
      divBackgroundImage = "https://sfwallpaper.com/images/android-central-wallpaper-23.jpg"
    ),
    title = list(
      style = list(
        color = 'white',
        fontFamily = "Open Sans"
      )
    )
  )
)
```

```{r}
#Below CSS helps to Customizing the dashboard color, tabset color, and font color.
```

<style>
.colored {
  background-color: #FAFAFA;
}
.navbar {
  background-color:#1c2b36;
  font-color:white:
  height:66px;
  position: fixed;
  z-index: 904;
  min-width: 320px;
  width:100%;
}
.navbar-brand {
color: #fff;
display: block;
font-size: 15px;
font-family: Roboto,sans-serif;
float: left;
}
body {
  padding-top:80px;
}
.navbar-default .navbar-nav>.active>a{
color: #ffffff;
background-color: #2727270f;  
}
.navbar-default .navbar-nav>.active>a:hover{
color: #1b867b;  
}

.nav-tabs{
 background-color:#1c2b36;
 font-color:#f5f5f5;
}
.nav-tabs-custom > .nav-tabs > li > a {
    color: #f5f5f5;
    font-weight: 300;
    font-size: 14px;
    border-radius: 0;
    padding: 3px 10px 5px;
    text-transform: none;
}
</style>



DashBoard
=============================================================================

Row {.tabset .tabset-fade data-width=1500 .colored }
--------------------------------------------------------



### Most Popular Categories {.no-padding}

```{r fig.height=8}
#The below plots shows the category wise most installed apps
data.clean %>%
  count(Category, Installs) %>%
  group_by(Category) %>%
  summarize(
    TotalInstalls = sum(as.numeric(Installs))
  ) %>%
  arrange(-TotalInstalls) %>%
  hchart('scatter', hcaes(x = "Category", y = "TotalInstalls", size = "TotalInstalls", color = "Category")) %>%
  hc_add_theme(dark) %>%
  hc_title(text = "Most popular categories (# of installs)")
```

### Top 10 Paid Categories {.no-padding}
```{r fig.height=8}
#It shows the category wise most installed paid app
data %>%
  filter(Type == "Paid") %>%
  group_by(Category) %>%
  summarize(TotalInstalls = sum(Installs)) %>%
  arrange(desc(TotalInstalls)) %>%
  head(10) %>%
hchart('column',hcaes('Category','TotalInstalls')) %>%
  hc_title(text = "Top 10 Paid Categories") %>% hc_add_theme(thm_dark)
```

### Most Popular Android Version {.no-padding}
```{r fig.height=8}
#Shows most popular android version by their count
df1%>%
  group_by(Android.Ver)%>%
  summarise(Count = n())%>%
hchart('column',hcaes('Android.Ver','Count')) %>%
  hc_title(text = "Most Popular Android Version") %>% hc_add_theme(thm)
```

Row { }
-----------------------------------------------------------------------

### Total No Of Installs </font>
```{r fig.height=20}
#Total number of app installation
# Create value box
valueBox(sum(data$Installs), icon = "fa fa-android", color = '#FAFAFA')
```

### Total Reviews

```{r fig.height=1.5}
#Total number of reviews
# Create value box
valueBox(sum(data$Reviews), icon = "fa fa-android", color = '#FAFAFA')
```

### Total Paid and Free Appss {.no-title .no-padding .colored }
```{r }
#Total Paid anf Free apps
df_type = subset(df1, (Type == 'Free' | Type == 'Paid'))

tt <- df_type%>%
  group_by(Type)%>%
  summarise(n = n())

highchart() %>%
  hc_add_series(tt, hcaes(x = tt$Type, y = tt$n), type = "pie") %>%
  hc_tooltip(borderWidth = 1.5, headerFormat = "", pointFormat = paste("<b>{point.Type} : {point.n}</b>")) %>%
  
  hc_title(
    text="Total Paid and Free Apps"
    ) %>%
  hc_add_theme(hc_theme_ffx())

```

Plotly 
========================================================================
Column { data-width=250}
-----------------------------------------------------------------------

### Filters {.no-title .colored }
**Pick filters here:**
```{r}

#Based on the filters(Ratings, Content ratings, Type of app) the below shows the below plots shows the number of installs category wise
filter_table<-data %>% select(Content.Rating, Type,Rating , Category,  Installs)  %>%
  group_by(Content.Rating, Type,Rating, Category)  %>%
  summarise(Total_Installs =sum(Installs))

shared_data <- SharedData$new(filter_table, group = 'hello')
#Input filter rating
filter_select("filter_content", "Content Rating", shared_data, ~Content.Rating, allLevels = TRUE, multiple = TRUE)

```

```{r }
#Input filter for ratings
filter_slider("filter_rating", "Ratings", shared_data, ~Rating, step = 1)
```

```{r }
#Input filter for App type
filter_select("filter_Type", "Free/Paid", shared_data, ~Type, allLevels = TRUE, multiple = TRUE)
```


**Data Table**
```{r}
#Datatable shows the value based on applied filters
# Create datatable. 
datatable(shared_data,
          rownames = FALSE,
          colnames = c('Content Type','Free/Paid','Rating','Category', 'Installs'),
          class = 'cell-border stripe',
          extensions = "Scroller",
          options=list(deferRender = FALSE, 
                       scrollY = 200, 
                       scrollCollapse = TRUE,
                       scroller = TRUE,
                       dom = 't'))
```

Column {data-width=750}
-----------------------------------------------------------------------

### 3D plot {.no-title .colored }
```{r fig.height=8}
#Plots shows value based on apllied filters

# Set a random seed. We will do this so that we can reproduce the random sample of colors we will use for our next graph. 
set.seed(80085)

fig <- plot_ly(shared_data, x = ~Rating, y = ~Total_Installs, z = ~Content.Rating, color = ~Category, colors = sample(colours(), 120))
fig <- fig %>% add_markers()
fig <- fig %>% layout(title = 'Rating, Content Type, Installs',scene = list(xaxis = list(title = 'Rating'),
                     yaxis = list(title = 'Total Installs'),
                     zaxis = list(title = 'Content Type')))
fig
```

Dataset
===================================================================

```{r}
#Interactive Datatable
datatable(data,
              options = list(
                  pageLength = 30
              ))
```

More Plots
===================================================================
Row
-------------------------------------
    
### Ratings vs Number Of Reviews
    
```{r}
#Scatter Plot Rating vs Reviews based on App type(Paid/Free)
hchart(data, "scatter", hcaes(x = Reviews, y = Rating, group = Type))
```

### Median Price Category

```{r}
data.clean %>%
  filter(Type == "Paid") %>%
  group_by(Category) %>%
  summarize(
    Price = median(Price)
  ) %>%
  arrange(-Price) %>%
  hchart('treemap', hcaes(x = 'Category', value = 'Price', color = 'Price')) %>%
  hc_add_theme(hc_theme_google()) %>%
  hc_title(text="Median price per category")
```
    
### Percentage of Free vs Paid  by Category

```{r}
data.clean %>% 
  group_by(Category, Type) %>%
  summarize(
    n = n()
  ) %>%
  mutate(perc = round((n /sum(n))*100)) %>%
  hchart('bar', hcaes(x = 'Category', y = 'perc', group = 'Type')) %>%
  hc_plotOptions(series=list(stacking='normal')) %>%
  hc_title(text="Percentage of Free vs Paid by Category") %>%
  hc_add_theme(hc_theme_flat())
``` 

    
### Distribution Of Application Size
    
```{r}
data.clean %>%
  count(Size) %>%
  hchart('area', hcaes(x = "Size", y = "n")) %>%
  hc_colors("#158cba") %>%
  hc_add_theme(hc_theme_gridlight()) %>%
  hc_title(text = "Distribution of application size (in MB)")
```
    


About {data-icon="fa-info-circle"}
===================================================================
Column {data-width=600}
-----------------------------------------------------------------------
**Google Play Store**

Google Play, originally designated by Google as Android Market, is the official Android apps, games, and other content store and portal for your Android-powered phone, tablet, or Android TV.
<br>
Just as Apple has its App Store, the Google Play Store is run by Google. It's an enormous place and it offers its users lots of content.
<br>Here I have created several visualization related to Google play store like top categories, total number of installs, top paid categories.
<br>

**Dataset**

The data set used to create the dashboard can be found at: 

https://www.kaggle.com/lava18/google-play-store-apps

Columns in Dataset
```{r}
str(data)
```


